Structure constants and short-time simulations of open collective quantum spin systems

### 2019-03-28 soc_squeezing/collective_paper/collective_spin.tex
greatly simplified the derivation for short-time linear response and two-time correlators

\section{Two-time correlation functions and non-equilibrium linear
  response}
\label{sec:TTC}

As a final example, we consider the calculation of two-time
correlation functions in a collective spin system.  These correlation
functions allow us to extract the short-time linear response of
Heisenberg operators to small perturbations of a collective spin
system's Hamiltonian.  Consider a target Hamiltonian $H$ perturbed by
an operator $V$, such that the net Hamiltonian is $\widetilde H=H+V$.
We denote the generator of Heisenberg time evolution under the
perturbed (unperturbed) Hamiltonian by $\widetilde T$ ($T$).  These
time evolution operators are related by
\begin{align}
  \widetilde T = T + \hat V
\end{align}
where $\hat V$ is a superoperator whose action on operators $\O$ is
defined by
\begin{align}
  \hat V \O \equiv i\sp{V,\O}_-.
\end{align}
By Taylor expanding through quadratic order in the time $t$, we can
find that for sufficiently small times
\begin{align}
  e^{t\hat V} e^{t T}
  \approx e^{t\widetilde T} - \f12 t^2 \sp{T,\hat V}_-.
\end{align}
To leading order in $\hat V$ and quadratic order in $t$, we therefore
have
\begin{align}
  e^{t\widetilde T} - e^{tT}
  \approx t\hat V e^{tT} + \f12 t^2 \sp{T,\hat V}_-,
\end{align}
where
\begin{align}
  \f12 t^2 \sp{T,\hat V}_- \approx \f12 t \sp{e^{tT}, \hat V}_-,
\end{align}
which implies
\begin{align}
  e^{t\widetilde T} - e^{tT} \approx \f12 t \sp{e^{tT},\hat V}_+.
\end{align}
Defining the perturbed and unperturbed Heisenberg operators
$\widetilde\O\p{t}\equiv e^{t\widetilde T}\O$ and
$\O\p{t}\equiv e^{tT}\O$, we thus find
\begin{align}
  \widetilde\O\p{t} - \O\p{t}
 \approx \f12 i t \p{\sp{V,\O\p{t}}_- + \sp{V,\O}_-\p{t}}.
\end{align}

>>>>

\section{Non-equilibrium linear response and two-time correlation
  functions}
\label{sec:NLR}

As a final example, we consider the calculation of two-time
correlation functions, which allow us to extract the short-time linear
response of Heisenberg operators to perturbations of a Hamiltonian.
Consider a target Hamiltonian $H$ perturbed by an operator $V$ with
$\norm{V}\ll\norm{H}$, such that the net Hamiltonian is
$\widetilde H=H+V$.  We denote the generator of Heisenberg time
evolution under the perturbed (unperturbed) Hamiltonian by
$\widetilde T$ ($T$).  These generators are related by
\begin{align}
  \widetilde T = T + i\hat V
\end{align}
where $\hat V$ is a superoperator whose action on operators $\O$ is
defined by
\begin{align}
  \hat V \O \equiv \sp{V,\O}_-.
\end{align}
Through quadratic order in the time $t$, we can say that
\begin{align}
  e^{t\widetilde T}
  \approx \f12\sp{e^{tT}, e^{it\hat V}}_+,
\end{align}
which at first order in the perturbation $\hat V$ implies
\begin{align}
  e^{t\widetilde T}
  \approx e^{tT} + \f12 i t \sp{\hat V, e^{t T}}_+.
\end{align}
Defining the perturbed and unperturbed Heisenberg operators
$\widetilde\O\p{t}\equiv e^{t\widetilde T}\O$ and
$\O\p{t}\equiv e^{tT}\O$, we thus find that for sufficiently small
times $t$ and weak perturbations $V$,
\begin{align}
  \widetilde\O\p{t}
  \approx \O\p{t} + \f12 i t \p{\sp{V,\O\p{t}}_- + \sp{V,\O}_-\p{t}}.
\end{align}
